Topic categorization in Portuguese news articles\\ \thanks{Fundação para a Ciência e Tecnologia}

### 2018-01-04 article.tex
spellcheck

\begin{abstract}
Categorizing news articles according to their contents allows to
decrease the information entropy in a world where the rate of
publication of digital text documents is increasing fast. In this
article we describe ongoing work which aims to evaluate the
feasability of implementing a classifier which is lightweight
enough to be used in real time on the client side of a web
application.  More specifially, we gathered a corpus of Portuguese
news and used it to train and evaluate several classification
algorithms. We analyze the results obtained in terms of the
classifiers error rate, traning time and memory footprint.
\end{abstract}

@@

Having the entire workflow happening within the digital world presents
some opportunities when compared to the traditional
process\cite{o1997comparison}. In particular, due to the current
processing power commonly available, tasks related to the manipulation
of the information contained within these documents (searching,
compiling, annotating, sharing, \dots) can now be performed
automatically and targetting a large amount of articles.

@@

\section{Methods}
In order to train and evaluate classification algorithms, we first
needed to choose and obtain a suitable dataset. Preferably, this
dataset would contain documents were already categorized, which would
allows to skip the time and effor-consuming step of manually
categorizing the articles ourselfs. Once this dataset was chosen and
obtained, we would then clean and prepare it to be used to train the
classifiers.

@@

We used the \texttt{removeSparseTerms} function from the \texttt{tm}
package, and produced three distinct lists of terms:
\begin{description}
    \item[$LT_{90}$] contained terms with 90\% or less sparcity
    \item[$LT_{95}$] contained terms whose sparcity was under 95\%
    \item[$LT_{99}$] contained the terms with a sparcity level below 99\%
\end{description}

>>>>

\begin{abstract}
Categorizing news articles according to their contents allows to
decrease the information entropy in a world where the rate of
publication of digital text documents is increasing fast. In this
article we describe ongoing work which aims to evaluate the
feasibility of implementing a classifier which is lightweight
enough to be used in real time on the client side of a web
application.  More specifically, we gathered a corpus of Portuguese
news and used it to train and evaluate several classification
algorithms. We analyze the results obtained in terms of the
classifiers error rate, training time and memory footprint.
\end{abstract}

@@

Having the entire workflow happening within the digital world presents
some opportunities when compared to the traditional
process\cite{o1997comparison}. In particular, due to the current
processing power commonly available, tasks related to the manipulation
of the information contained within these documents (searching,
compiling, annotating, sharing, \dots) can now be performed
automatically and targeting a large amount of articles.

@@

\section{Methods}
In order to train and evaluate classification algorithms, we first
needed to choose and obtain a suitable dataset. Preferably, this
dataset would contain documents were already categorized, which would
allows to skip the time and effort-consuming step of manually
categorizing the articles ourselves. Once this dataset was chosen and
obtained, we would then clean and prepare it to be used to train the
classifiers.

@@

We used the \texttt{removeSparseTerms} function from the \texttt{tm}
package, and produced three distinct lists of terms:
\begin{description}
    \item[$LT_{90}$] contained terms with 90\% or less sparsity
    \item[$LT_{95}$] contained terms whose sparsity was under 95\%
    \item[$LT_{99}$] contained the terms with a sparsity level below 99\%
\end{description}
